The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-05 Paper.Rmd
a few more edits on same section

Our model with environmental effects which differed in the
two tails produced simulated ecological variables with visually apparent asymmetry 
of tail dependence and non-N copula structure (Fig. \ref{fig_ms_asym_b_0.1}).
Model selection results (Table \ref{SM-tab_summary_stat_asym_sens}) and
our nonparametric statistics (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_2}) statistically confirmed the visual result.
We repeated our analyses with $b=-0.1, 0.9, -0.9$, with similar conclusions
in all cases.
<!--***DAN: Right Shya? I have written this, but I want you to show me these results
(without putting them in the paper) to make sure the statement is accurate-->

>>>>

Our model with environmental effects which differed in the
two tails produced simulated ecological variables with visually apparent asymmetry 
of tail dependence and non-N copula structure (Fig. \ref{fig_ms_asym_b_0.1}).
Model selection results (Table \ref{SM-tab_summary_stat_asym_sens}) and
our nonparametric statistics (Tables \ref{SM-tab_stat_npa_asym_1} -\ref{SM-tab_stat_npa_asym_2}) statistically confirmed the visual result.
We repeated our analyses with $b=-0.1, 0.9, -0.9$, with similar conclusions
in all cases.
<!--***DAN: Right Shya? I have written this, but I want you to show me these results
(without putting them in the paper) to make sure the statement is accurate.
But we should put the figs in the sup mat, not the stats results, I think, but we could put the figs-->
